---
title: "Data and control structures 2"
author: "Dominik Pegler"
date: '2022-04-25'
output: html_document
---

##*Control structures in R*

*if statements in R*
```{r if statements in R}
#general if statement
# if (test_expression) {
#   statement
# }
#example
x <- 5

if (x > 0) {
  print("Positive number")
}

#general if...else statement
# if (test_expression) {
#   statement1
# } else {
#   statement2
# }

#example
if (x >0) {
  print("Positive number")
} else {
  print("Negative number")
}


#if...else Ladder: execute a block of code among more than two alternatives
# if (test_expression1){
#   statement1
# } else if (test_expression2) {
#   statement2
# } else if (test_expression3) {
#   statement3
# } else {
#   statement4
# }

y <- -1
x <- -2
#example
if (x > 0 & y > 0) {
  print("ONE")
} else if (x < 0 | y < 0) {
  print("TWO")
} else {
  print("THREE")
}

```

```{r Exercise}
#Create x and y, and assign both of them a single number each!
#Now write an if statement: You want R to print the message "both low" if x and y are both smaller than 4, to print the message "x low, y high" if x is smaller than 4 and y bigger or equal than 4, to print "x high, y low" if y is smaller than 4 and x is bigger or equal 4, to print "both high" if both are bigger or equal 4, and to print "not applicable" if none of this is true (is there a case?). 
```


*Applying if statements to our dataframe*

```{r applying if statements to dataframes}
#read in the dataframe if you cleared your workspace
df1 <- read.csv("data/Example_data.csv", header =TRUE, sep = ",")
#View(df1)
#I want to create a new variable that divides the faces into high and low groups

#Problem: if...else if... can only react to one locigal vector at the same time

#if Attractiveness is lower than 4, give new variable the value low. If Attractiveness is higher or equal to 4, give new variable the value high.

if (df1$AttractivenessPicture < 4) {
  df1$Group = "low"
} else {
  df1$Group = "high"
}

#prints this warning: "the condition has length > 1 and only the first element will be used"

#use ifelse instead (the vectorized form of if....else)
#ifelse(test, yes, no)

df1$Group <- ifelse(df1$AttractivenessPicture <4, "low", "high")

#Nested ifelse statements: add two more options: 4 as medium and NAs
df1$Group <- ifelse(df1$AttractivenessPicture <4, "low",
                    ifelse(df1$AttractivenessPicture ==4, "medium",
                           ifelse(df1$AttractivenessPicture >=4, "high", 
                           NA)))
```


*for loops in R*
* A loop is a way to repeat a sequence of instructions under certain conditions
* It allows you to automate parts of your code that are in need of repetitions
* iteration over a vector

```{r for statements in R}
#general for loop
# for (val in sequence){ #sequence is a vector, val the single values of the vector
#   statement
# }

#example
x <- c(2,5,3,9,8,11,6)
for (val in x) {
print("yes")
}

#you can also add more statements (commands) within the brackets
for (val in x) {
doubleval <- val*2
print(doubleval)
print("yes")
}

#indexing and looping
for (i in 1:length(x)){
doubleval <- x[i]*2
print(doubleval)
}

```

*Combining if statements and for loops in R*
```{r combining if statements and for loops}
for (i in 1:length(x)) {
  ifelse(x>3, print("x"), print("y")) 
}

#for dataframes
df1 <- read.csv("data/Example_data.csv", header =TRUE, sep = ",")

for (row in 1:nrow(df1)) {
    Attractiveness <- df1[row, "AttractivenessPicture"]
    Averageness  <- df1[row, "AveragenessPicture"]

    if(Attractiveness> 3) {
        print(paste("With an averageness rating of", Averageness, 
                    "the attractiveness rating was", Attractiveness))
    }
}

#for loops over columns with col and ncol
```

*The break statement*
* The R Break statement is very useful to exit from any loop such as For Loop, While Loop, and Repeat Loop
* While executing these loops, if R finds the break statement inside them, it will stop executing the statements and immediately exit from the loop.
```{r the break statement}
x <- c(2,5,3,9,8,11,6)
#without the break statement R will execute all commands (will also show the text, but will continue afterwards)
for (val in x)  {
  if (val == 9)  {
    print(paste("Stop the loop because the defined value is reached where i=  ", val))
  }
  print(paste("Values are :  ", val))
}

#with break statement R will execute all commands unti the break statement is true and will then not continue anymore
for (val in x)  {
  if (val == 9)  {
    print(paste("Stop the loop because the defined value is reached where i=  ", val))
    break
  }
  print(paste("Values are :  ", val))
}
```

