---
title: "H10 - Visualization II"
author: "Dominik Pegler"
output:
  html_document:
    df_print: paged
---

All examples should be done using ggplot2 (tidyverse). Also, in all examples, the axes should be labeled appropriately using xlab() and ylab().

```{r}
library(ggplot2, tidyverse)
theme_set(theme_minimal())
update_geom_defaults("bar", list(fill = "steelblue", alpha = 0.4))
update_geom_defaults("point", list(color = "steelblue", alpha = 0.4, size = 2.6))
update_geom_defaults("boxplot", list(fill = "steelblue", alpha = 0.4))
```


## 1) Make a bar plot ...

... of mean fuel efficieny (hwy) over the levels of cyl. In addition: dodge the bar plots according to the variable class. Color code the dodged bar plots  (according to class) and and use a legend for the color code. (Hint: Use stat="summary", fun="mean" in geom_bar, or possibly "fun" instead of "fun.y" depending on your version of ggplot). Additional tip: color = "black" makes the borders of the bars more salient. 

[1 point]

```{r}
ggplot(data = mpg, mapping = aes(x = as.factor(cyl), y = hwy)) + geom_bar(aes(fill = class), color = "grey", stat="summary", fun="mean", position = "dodge") + xlab("Number of cylinders") + ylab("miles per gallon (highway)")
```
