---
title: "H2"
output: html_notebook
---

Please generate the following vectors (without typing every single element). You can reach 1 point per exercise, 6 points in total. 

a) 5  10  15  20  25
b) 0  2  4  6  8  10  8  6  4  2  0
c) a  a  a  b  b  b  b c  c  c  c  c
d) 1  3  3  3  7  7  7  7  7  7  7  7
e) Convert the vector from example c) into a factor with the levels c, b, a (in this order). 
f) Add the vector from example c) to the vector from example d) by converting a to 1, b to 2, and c to 3. 

Tipp: In the last session, we learned functions like rep() or seq() - they might be helpful ;)

Create a RNotebook and please upload your .html file (and maybe also your .Rmd file) to Moodle until Sunday, 27th March 2022, 11:59 pm.

## Task a

```{r}
vec_a <-seq(5,25, by=5)
vec_a
```


## Task b

```{r}
vec_b <- c(seq(0,10, by=2),seq(8,0, by=-2))
vec_b
```

## Task c

```{r}
vec_c <- c(rep(letters[1],3),rep(letters[2],4),rep(letters[3],5))
vec_c
```


## Task d

```{r}
vec_d <- c(rep(1,1),rep(3,3),rep(7,8))
vec_d
```

## Task e

```{r}
vec_e <- factor(vec_c, levels=rev(unique(vec_c)))
vec_e
```

## Task f

```{r}
vec_c_num <- as.numeric(factor(vec_c, levels=c('a','b','c'), labels = c(1,2,3)))
vec_f <- vec_c_num + vec_d
vec_f
```

