---
title: "H5"
author: "Dominik Pegler"
output:
  html_document:
    df_print: paged
---

Please address the following questions and tasks and upload your R Notebook in html format (1 point per question):

Deadline: Sunday, 24th April, 23:59 pm

## Task 1: Read in the csv file from Moodle (Example data)

```{r}
file_path ="data/Example_data.csv"
df <- read.csv(file_path)
```

## Task 2: What are the variable names?
```{r}
names(df)
```
## Task 3: What is the mean of the variable "DominancePicture"?

Here you can use different approaches to get the solution!
```{r}
mean(df$DominancePicture, na.rm = TRUE)
```

## Task 4: Change the Trial_Id variable to a factor 
```{r}
df$Trial_Id <- as.factor(df$Trial_Id)
str(df$Trial_Id)
```


## Task 5: Add a new column to the dataset

Use the cbind() function for this. The new column should be all numbers from 1 to 40 (extra point: numbers are in a randomized order). For help on the function call ?cbind or use Google ;)
```{r}
df$New_Col <- cbind(sample(seq(1:40)))
str(df$New_Col)
```

## Task 6: The function duplicated()

is used to detect duplicates (e.g. same row is twice in your data). Interpret the output in one sentence when applying it to the data set

```{r}
df[duplicated(df),]
```

Interpretation: There are no duplicate rows

```{r}
df[duplicated(df$DominancePicture),]
```

Interpretation: There are 33 rows that have non-unique values for the variable DominancePicture

