---
title: "H6"
author: "Dominik Pegler"
output:
  html_document:
    df_print: paged
---

Deadline:  Sunday, 1st May 2022, 11:59pm

## 1. Create a dataset ...

... that contains three variables: variable "subject_ID" shall contain the numbers from 1 to 40 in a chronological order. Variables "rating_1" and "rating_2" shall contain rating responses from a 7-point Likert scale (think about what this means for the probable ditribution of the data...).  

(1 Point)

```{r}

N <- 40

subject_ID <- seq(1:N)

# for a 7-point likert scale, we assume normal distribution
# which we simulate with the following probability distribution

likert_7 = 1:7

# prob_7_likert <- c(1/7, 1/7, 1/7, 1/7, 1/7, 1/7, 1/7) # uniform 
prob_likert_7 <- c(0.25/7, 0.5/7, 1.5/7, 2.5/7, 1.5/7, 0.5/7, 0.25/7) # normal

rating_1 <- sample(likert_7, N, replace = TRUE, prob = prob_likert_7)
rating_2 <- sample(likert_7, N, replace = TRUE, prob = prob_likert_7)

# creating the dataframe 
df <- data.frame(subject_ID)
df$rating_1 <- factor(rating_1, order=TRUE, levels = likert_7)
df$rating_2 <- factor(rating_2, order=TRUE, levels = likert_7)
head(df)
```

```{r}
# import ggplot and set some defaults
library(ggplot2)
theme_set(theme_minimal())
update_geom_defaults("bar", list(fill = "steelblue"))

ggplot(df, aes(x=rating_1)) +
  scale_x_discrete(drop=FALSE) +
  geom_bar()
```

```{r}
ggplot(df, aes(x=rating_2)) +
  scale_x_discrete(drop=FALSE) +
  geom_bar()
```

## 2. Create another variable ...

... ("level") based on the two rating variables. The variable should be a string variable and should contain the value "1 higher" when rating_1 is higher than rating_2, it should contain the value "2 higher" when rating_2 is higher than rating_1, and it should contain the value "equal" when both ratings contain the same value.   

(1 Point)

```{r}
df$level = "equal" # inital value for all rows
df[df$rating_1 > df$rating_2, "level"] <- "1 higher"
df[df$rating_1 < df$rating_2, "level"] <- "2 higher"
head(df)
```

```{r}
ggplot(df, aes(x=level)) +
  scale_x_discrete(drop=FALSE) +
  geom_bar()
```

## 3. Calculate ... 
... the value z from the values x and y with this formula: z = x/y. To do this calculation, you need to specify some traits for x and y. Tipp: which class is need to calculate sth? What does basic mathematic tell us about divisions? What is not possible? Put all these requirements in an if statement so that R will only conduct the calculation if these requirements are met. R should also tell you when it couldn't do the calculation! Give two examples: one, where R will calculate and one, where R will not calculate.  

(2 Points)

```{r}
# create some random x and y values with y based on the level variable (just to make some use of it :) )

# x: random int values between 0 and 5 and a few missing values

df$x <- sample(-1:5,N, replace = TRUE)
df[df$x == -1, "x"] <- NA

# y

# these ones will get a problematic 0 as divisor
df[df$level == "2 higher", "y"] <- 0
# these ones will get a useful divisor (int between 1 and 5)
df[df$level == "1 higher", "y"] <- sample(1:5, length(df[df$level == "1 higher", "y"]), replace=TRUE)
# all the others with level == "equal" will have problematic missing values

head(df)
```



```{r}
for (i in 1:nrow(df)) {
  x_ = df[i,"x"]
  y_ = df[i,"y"]
  
  cat("Row",i,"\tx:",x_,"\ty:",y_,"\t")
  
  if (is.na(x_) | is.na(y_)) {
    cat("z: - \tMissing value(s)")
  } else if (y_ == 0) {
    cat("z: - \tDivision by 0")
  } else {cat("z:",x_/y_)}
  
  cat("\n")
}
```

```{r}

# when we create the column z, we get all possible results, for the 
# problematic cases R will give us 'Inf' (div by 0), NA (missing
# values) and 'NaN' (0 div by 0) 

df$z <- df$x / df$y
head(df)
```


## 4. Use a for loop ...
... to calculate the sum of rating_1 and rating_2 for each subject_ID and save it in a new column "rating_sum".

(1 Point)

```{r}
for (i in 1:nrow(df)) {
  
  # includes the necessary conversion back to integers since rating_1 and rating_2
  # are ordered factors
  df[i,"rating_sum"] = as.numeric(df[i,"rating_1"]) + as.numeric(df[i,"rating_2"])

}

head(df)

```

## 5. Tell ...
... why is the approach in exercise 4 not the best? What would have been a better solution to calculate the variable? Explain and give alternative calculation.

(1 Point)

Answer:

I would assume that for-loops in R are slow and you have to handle the exceptions (division by zero, missing values) yourself, as opposed to built-in, already optimized (c/c++ under the hood?) vector functions with standard behaviour for exceptions.

```{r}
df$rating_sum_v <- as.numeric(df$rating_1) + as.numeric(df$rating_2) 
head(df)
```



