---
title: "H9 - Visualization"
author: "Dominik Pegler"
output:
  html_document:
    df_print: paged
---

All examples should be done using ggplot2 (tidyverse). Also, in all examples, the axes should be labeled appropriately using xlab() and ylab().

```{r}
library(ggplot2, tidyverse)
theme_set(theme_minimal())
update_geom_defaults("bar", list(fill = "steelblue", alpha = 0.4))
update_geom_defaults("point", list(color = "steelblue", alpha = 0.4, size = 2.6))
update_geom_defaults("boxplot", list(fill = "steelblue", alpha = 0.4))
```


## 1) Make a scatterplot ...

... of hwy (y-axis) vs. cyl (x-axis) from the dataset mpg (from tidyverse). 

[1 point]

```{r}
ggplot(mpg, aes(x = cyl, y = hwy)) + geom_point() + xlab("Number of cylinders") + ylab("miles per gallon (highway)") + 
  stat_smooth(method = "lm", color = "steelblue")
```


## 2) Add jitter ...

... to the scatterplot from example (1) to avoid overplotting. 

[1 point]

```{r}
ggplot(mpg, aes(x = cyl, y = hwy)) + geom_jitter() + xlab("Number of cylinders") + ylab("miles per gallon (highway)")
```


## 3) Can you ...

... avoid plotting the empty category of 7 cylinders in examples (1) and (2)? (Me: And differentiate each class by color.)

[1 point]

```{r}
ggplot(mpg, aes(x = factor(cyl), y = hwy, color = class)) + geom_jitter() + xlab("Number of cylinders") + ylab("miles per gallon (highway)")
```


## 4) Use boxplots ...

... for each level of cyl to visualize the distribution of hwy. (Hint: cyl should be treated as a factor using as.factor().) 

[1 point]

```{r}
ggplot(mpg, aes(x = factor(cyl), y = hwy)) + geom_boxplot() + xlab("Number of cylinders") + ylab("miles per gallon (highway)")

```

## 5) Overlay the plots ...

... of example (2/3) and (4). Use a different color for the points from plot (2). (Hint: Plot the scatterplot over the boxplots to make all the points visible.)

[1 point]

```{r}
ggplot(mpg, aes(x = factor(cyl), y = hwy)) + geom_boxplot(fill = "white") + geom_jitter(alpha = 0.25) + xlab("Number of cylinders") + ylab("miles per gallon (highway)")

```

